\newpage
\begin{thebibliography}{99}
\addcontentsline{toc}{section}{参考文献}

\bibitem{survey}
J. Zhang, Y. Li, A. Chen, et al.
\newblock Advances in Feed-Forward 3D Reconstruction and View Synthesis: A Survey.
\newblock \emph{arXiv preprint arXiv:2507.14501}, 2025.

\bibitem{dust3r}
S. Wang, V. Leroy, Y. Cabon, B. Chidlovskii, and J. Revaud.
\newblock DUSt3R: Geometric 3D Vision Made Easy.
\newblock \emph{CVPR}, 2024.

\bibitem{vggt}
J. Wang, M. Chen, N. Karaev, A. Vedaldi, C. Rupprecht, and D. Novotny.
\newblock VGGT: Visual Geometry Grounded Transformer.
\newblock \emph{CVPR}, 2025.

\bibitem{cut3r}
Q. Wang, Y. Zhang, A. Holynski, A. A. Efros, and A. Kanazawa.
\newblock Continuous 3D Perception Model with Persistent State.
\newblock \emph{CVPR}, 2025.

\bibitem{easi3r}
X. Chen, Y. Chen, Y. Xiu, A. Geiger, and A. Chen.
\newblock Easi3R: Estimating Disentangled Motion from DUSt3R Without Training.
\newblock \emph{ICCV}, 2025.

\bibitem{flare}
H. Zhang, et al.
\newblock FLARE: Feed-Forward Geometry, Appearance and Camera Estimation from Uncalibrated Sparse Views.
\newblock \emph{arXiv preprint}, 2025.

\bibitem{vggtomega}
J. Wang, M. Chen, S. Zhang, et al.
\newblock VGGT-$\Omega$: Scaling Feed-Forward 3D Reconstruction.
\newblock \emph{arXiv preprint}, 2026.

\bibitem{3dgs}
B. Kerbl, G. Kopanas, T. Leimkuehler, and G. Drettakis.
\newblock 3D Gaussian Splatting for Real-Time Radiance Field Rendering.
\newblock \emph{ACM Transactions on Graphics}, 42(4), 2023.

\bibitem{trellis}
J. Xiang, Z. Lv, S. Xu, et al.
\newblock Structured 3D Latents for Scalable and Versatile 3D Generation.
\newblock \emph{arXiv preprint arXiv:2412.01506}, 2024.

\bibitem{trellis2}
J. Xiang, X. Chen, S. Xu, et al.
\newblock Native and Compact Structured Latents for 3D Generation.
\newblock \emph{arXiv preprint arXiv:2512.14692}, 2025.

\bibitem{vggtedit}
K. Zhu, Y. Tang, Y. Yang, et al.
\newblock VGGT-Edit: Feed-Forward Native 3D Scene Editing with Residual Field Prediction.
\newblock \emph{arXiv preprint}, 2026.

\bibitem{rl3dedit}
J. Wang, C. Lin, L. Sun, et al.
\newblock Edit in 2D, Verify in 3D: Reinforcement Learning for Multi-view Consistent Scene Editing.
\newblock \emph{arXiv preprint}, 2026.

\bibitem{realm}
C. Shi, M. Chen, Y. Mao, et al.
\newblock REALM: Reasoning Segmentation and Editing in 3D Gaussian Scenes with MLLM Agents.
\newblock \emph{arXiv preprint}, 2026.

\bibitem{vinedresser}
Y. Chi, X. Li, Z. Huang, and J. M. Rehg.
\newblock Vinedresser3D: Agentic Text-guided 3D Editing.
\newblock \emph{arXiv preprint arXiv:2602.19542}, 2026.

\bibitem{twintex}
W. Xiong, H. Zhang, B. Peng, et al.
\newblock TwinTex: Geometry-aware Texture Generation for Abstracted 3D Architectural Models.
\newblock \emph{ACM Transactions on Graphics}, 42(6), 2023.

\bibitem{syncity}
P. Engstler, A. Shtedritski, I. Laina, C. Rupprecht, and A. Vedaldi.
\newblock SynCity: Training-Free Generation of 3D Worlds.
\newblock \emph{arXiv preprint arXiv:2503.16420}, 2025.

\end{thebibliography}
